\documentclass[]{report}


% Title Page
\title{ASSIGNMENT 5}
\author{KAHIGIRIZA PETER WARREN		216002577		16/U/5173/PS\\
		AINEBYONA DONALD			216013093		16/U/2970/PS\\
		KYOBWEINE PRISCA			216002579		16/U/6489/PS\\
		KIZITO EZEKIEL				213012200		13/U/6970/EVE}


\begin{document}
\maketitle \underline{{\scriptsize TRACKING DAILY CONSISTENCE OF ATTENDANCE		
		 FOR STUDENTS OF COMPUTER SCIENCE}}
}


\begin{flushleft}
\underline{Introduction}\linebreak
	
	Makerere University is one the greatest institutions in the country Uganda and by far the world all over. It’s however characterized by a number of colleges of which these are made of different course programs. The programs that in turn are assigned to students of various backgrounds based on their qualifications run for a specific duration for a given program, each student studies and eventually graduates at this great institute.\linebreak
	
	 However, what exactly happens on ground is what the main focus is about; daily consistence of lecture attendance for students offering computer science.
	There is necessarily a need to dig deep into the college of computing and information sciences which requires the highest standards of attendance from all students in the different course programs.\linebreak
	
	 This is so because they may develop their full potential during their time of study.  The main aim of this research problem is to maintain a culture of excellence, attendance and punctuality.  Over the years, inconsistence in attendance for lectures has had a negative significant effect on students as well as their life opportunities.\linebreak
	 
	   All the parties associated with the college especially students and lecturers as well as support staff and external agencies to some point do all they can to ensure that excellent attendance and punctuality is maintained at the college.\\
	
	The need to provide education of higher standards for all students and necessity to devise a platform that may require all  students to  feel  valued  and  welcome is what anticipates making the college a successful learning environment. Lecturers and students play a major role in making the college what it is. Thus, this shared responsibility is what promotes an excellent lecture attendance and punctuality in terms of consistence.\linebreak
	
	As intended, the goal is to boost a 100\% attendance  for  all  students and to some extent all the lecturers so that every opportunity will be used to convey to them the importance of consistent and punctual attendance. This therefore will better progress, both socially and academically; ease with adjusting to college routines, lecture assignments and course works; satisfying learning and also minimization on “half-baked” students with regards to practicability hence producing upright and trained personnels.
	
\end{flushleft}
\end{document}          
